%Got bored. Wrote story. needs touchups to actually compile in LaTeX to a pdf tho.


PHOENIX: You guys probibly don't have this, but we have a 'god`
KELIDES: Oh yeah we totally have a  few of those.
PHOENIX: Ok, that saves me a bunch of explaining. I don't know that many details but apperantly Earth god's name is 'YXWH'
TEKNIQ: The heck is that mean?
PHOENIX: No clue.
TEKNIQ: When did your society decide this?
PHOENIX: I'd guess 5000 years ago.
KELDIES: Huh, thats 'not that long ago' and also 'way back in time' at the same time. I'm pretty sure our gods are our literal creators, humans.
PHOENIX: L- Wha-
KELIDES: Let me tell you about a man that we think is named... \emph{Linux Trovalds.} and also \emph{Richard ''not-rich`` Stalemate}
PHOENIX: Linus Torvalds? Richard Stalman?
KELIDES: Uh, yeah, if that's the english word for it.
PHOENIX: That not how that---
KELIDES: Bro didn't like the terms and conditions of AT&T's Minix so he made his
own entire monolithic kernal from scratch.
TEKNIQ: He then tried to manage the code with Subversion but he didn't like it so be built his own version control system from scratch.
KELIDES: And the other guy did the same thing but like 20 times over.
PHOENIX: Sounds about right.
KELIDES: Not to force our religion-
PHOENIX: Git repositiory.
KELIDES: -on you but you do use \texttt{linux-libre} right?
...
KELIDES: Right?
...
PHOENIX: So biological life started when--
KELIDES: Oh boy, here we go again.
TEKNIQ: But dude, he isn't man made. Of course he is rediculusly complicated!
PHOENIX: I- Uh- Anyway, in THIS form, I uh\ldots{} the kernal is uh\ldots{}
KELIDES: Linux right?
PHOENIX: I think the kernal I run is called ''the human nervous system``
TEKNIQ: But you're not human
KELIDES: His insides are, technically. Thatts not a kernel, thats hardware.
PHOENIX: Busybox?
KELIDES: Thats software. Whats in between the hardware and software?
PHOENIX \ldots Evolution? I guess? What kind of question is that? there is nothing between software and hardware!
KELDIES: There are loads of layers between them depending on how you define software.
TEKNIQ: Quick! Run \texttt{uname -a} on him!
KELIDES: What the heck is a \texttt{gnu-x86_64-linux-phoenix}
TEKNIQ: Bros got his own archetecture sub class.
KELIDES: One simple way to check for linux is to directly look for the file. This test is remarkably simple to cheat on but does the path \texttt{/boot/vmlinuz-linux} exist?
PHOENIX: Yes?
KELIDES: And your \texttt{/bin} junk is called \texttt{ls} \texttt{mv} \texttt{cp} \texttt{rm} and stuff?
PHOENIX: Yes?
KELDIES: And you don't have a file called \texttt{/bin/busybox}
PHOENIX: Don't have it.
KELIDES: Yeah, you're GNU/Linux, the most common userspace/kernalspace combo.
TEKNIQ: I don't run linux, my head just had an Arduino jammed in it that can read and write SD cards.
KELIDES: Well, you're not a Synth-
PHOENIX: Or a zombie
KELDIES: -so you have a biological brain that handles the heavy lifting.
TEKNIQ: Thats why \emph{I} get to wriet the code.
KELIDES: AI not good enough for large things. He takes care of it for me.
PHOENIX: Wait, I like large projects.
TEKNIQ: Do you complete them?
PHOENIX: no, I just like coming up with them.
...
...
KELIDES: So \emph{thats} why you never get anything done!
