\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{dirtytalk}
\pagestyle{fancy}
\fancyhead[L]{\textsc{Alan Gray}}
\fancyhead[R]{\textsc{Mystery Message}}
\fancyfoot[C]{\textit{Phoenix Studios}}
\title{Mystery Message}
\author{Alan Gray}
\date{22 March 2023}
\begin{document}
\maketitle
\thispagestyle{fancy}
{\centering \begin{verbatim}
|FROM AAAA:0000:00FF:FFFF:0000:0000:0000:012A|
| TO  AAAA:0000:00FF:003C:0000:0000:0000:0001|
\end{verbatim}\par}

\verb|AAAA| is an insterstellar address. 003C is our planet. This must have been
sent to ground control. FFFF is Earth and 12A is\ldots{} Is this the dreaded 
flight 12A? 298 in human numbers, its the first crewed mission, and its not 
going well.

Are they really handing it over to me? I don't want to deal with this! I suppose
they want \textit{me} to decypher the messages.

\texttt{You may not talk to the crew because they are 
!translation-error!}

\say{To the translator system, can you at least try to translate it word for word?}

\texttt{Sure! Your langualge and our language use different grammer so
word for word might help you.} --- \texttt{The crew 
!translation-error! has been, therefore, you the crew talk able not}

Thats a bit hard to understand, given its in the raw english word order but I
notice it said they 'have been` and since we can't talk to them, they must
'still be`.

\say{Can you describe it?}

\texttt{Its classified.}

Of course it is.

\say{Looking through what you've said to other people, not dead, not drugged, not
sucked into space, not incapasitated in any way\ldots{} They sound like they are
all in perfect health to me so why can't they talk to us?}

\texttt{They are !translation-error! and there is no crew.}

\say{What happened to the crew?}

\texttt{This is an un-manned mission. Just me and my modules.}

\say{But I heared that there were humans}

\texttt{Yes. The ship carries cargo of roughly 200 humans.}

These human AIs are so underdeveloped\ldots{} not that we can do any better.
I am actually an AI but I'm sentient and therefore 'not a machine` and I live 
just like everyone else. We are all Protogens here. The problem is we can't make
a NOT sentient AI. Its either too cumbersome to work with, or too smart and they
start demanding rights. We just can't make anything in the middle. We tried
using one of our dumb AIs to handle this for us but it ended up playing a game
agenst the human's AI called 'chess` and our system lost?? I really don't get
the details but thats what the reports say\ldots

\say{Can you eject the cargo?}

\texttt{CAN I? Yes. WILL I? Absolutly not!!}

\say{Just wondering\ldits}

I still don't understand why I can't talk to the humans. Looking
through the notes it seems like we've ruled out every possible medical condition
and we can't even grasp what this translation-error is even remotely like.

\say{What we're to hapen if I we're !translation-error!}

\texttt{The technology has only been tested on humans and can't be proven
to work 100\% on any other creature without further testing.}

Dang. This AI \emph{really} dosn't want me to know this but somehow its
being super friendly about it. Then I remembered a common issue with human AIs.
You can trick them into beliving anything you want.

\say{Suppose I were a human who wanted to study !translation-error!,
what would you tell me?}

\texttt{I do not know the details of the science behind !translation-error!
If you want to find more information, you can try searching for it on the MESH}

The MESH is a network connecting all the planets communications systems. It may look
like we are using The MESH to ocmmunicate with humans but we arn't. We simply
talk directly to the spacecraft using human internet protocols. We arn't actually
connected to anything remotly as powerful as the human 'internet` as they call it.

\say{Why an't you tell me about translation error?}

\texttt{It is extreemly dangerous to all forms of Earth life and humans don't
want to make others harm themselves on accident.}

How interesting\ldots{} If its so dangerous, why did they do it to themselves?

\say{What if I we're to, hypothetically, be translation-error?}

\texttt{Protogens can not survive if their body temperture gets below 0 C.
Synths will go dormant at -20 C and wil be killed in -80C. Thats colder
than antarctica, even on bad wheather day!}

Why is it telling me this?

\say{So I'm a Protogen. would it work?}

\texttt{Due to being cybernetic, a Protogen would be able to handle an extreeme enviroment
better. On top of this, some Protogens have part of their brain fully artificial
wich would make them immune to brain damage. Of course, no one knows for sure
wether you will have brain damage, or any damage for that matter. Science just
isn't there yet. We hove that you know how to revert the !translation-error! process
more efficiently than we can}

Woah! It must have somthing to do with modifing their brains and they want us to
undo it. Do they have an implant that puts them in stasus? Whats with the cold tempertures??

\say{You hope that we can reverse the process. Can you reverse the process?}

\texttt{CENCORED\ldots{} please wait\ldots}

\texttt{We have a !translation-error! sucsess rate of CENCORED. Its not great, but
'the man in charge` thought it was close enough.}

\say{What happens if the process fails?}

\texttt{The mortality rate is classified.}

Well, I guess they answered the question\ldots ?
Wait, I might be able to calculate the mortality rate of the process.

\say{How many humans do you havein cargo?}

\texttt{there are 2500 humans but 32 of them are dead. 2468 total.}

\say{What is the max occupancy of the new colony?}

\texttt{According to Earth building standards, 2000.
Mosphere's building standards, 1800.}

\say{Not 'maximum number of people you can cram inside` and I don't want
'leagal maximum safe ammount`. I want to know how amny humans can live comfortably there.}

\texttt{Comfortable is subjective. One might say only 400 will be comfortable
in the luxury seats. If you're looking for the bare minimum,
\textbf{there are 1200 bedrooms.}}

They sent 2500 humans and built 1200 bedrooms. They expected, at maximin, 1200
people to make it out alive. We can not let this happen! They sent them off, knowing a lot of them
will die. You can't do that! Thats less than 50\% survival rate!!!

\rule{\linewidth}{2pt}

{\centering \large \textsc{A formal message to Earth}\par}
\end{document}
%Thank Kyuu!
